environmental_data_preperation

### 2018-09-17 src/biological_data_prep.Rmd
extracting value to point....

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
Th
```{r pre-install packages, message=FALSE}
packages <- c("packrat", "rworldmap", "dplyr","plyr", "rgdal", "sp",)
source("../src/ipak.R")
ipak(packages)
suppressMessages(ipak)
```

@@

# createa unique cell ID

>>>>

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
Th
```{r pre-install packages, message=FALSE}
packages <- c("packrat", "rworldmap", "dplyr","plyr", "rgdal", "sp", "raster")
source("../src/ipak.R")
ipak(packages)
suppressMessages(ipak)
```

@@

# create a unique cell ID

A unique cell ID layer has been created in the environmental_data_preperation.Rmd. Now you want to extract the value of that layer to the .csv you are creating...

Load the env. data
```{r}
library(raster)
cell_layer <- raster("../output/env/unique_cell.tif") #this is loading the cell layer that was created and saved as a tif
plot(cell_layer)
```
The occurrence data needs to be converted into s spatialpoints dataframe
```{r}
library(sp)
xy <- adddata[ ,c(2,3)]
spatial_data <- SpatialPointsDataFrame(coords = xy, data = adddata, proj4string = CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"))
spatial_data
```
ok now you should probably reproject the data into the same projection as the env. data
```{r}
spatial_data_aea <- spTransform(spatial_data, CRS = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs") #note -60 used to be -91. Changed to 'straighten up'
```
Ok now plot the env. and point data...
```{r}
plot(cell_layer)
plot(spatial_data_aea$decimalLatitude, spatial_data_aea$decimalLongitude)
plot(spatial_data$decimalLongitude,spatial_data$decimalLatitude)
```
oh it doesn;t work... it should be in meters now?

### 2018-09-17 src/environmental_data_preperation.Rmd
extracting value to point....

now give a unique ID to each cell
```{r}
unique_cell[unique_cell > 0] <- 1:6731
writeRaster(unique_cell,'../output/env/unique_cell1.tif',overwrite=TRUE, options=c('TFW=YES')) #this is just to test it in ArcGIS
```

>>>>

now give a unique ID to each cell
```{r}
unique_cell[unique_cell > 0] <- 1:6731
writeRaster(unique_cell,'../output/env/unique_cell.tif',overwrite=TRUE, options=c('TFW=YES')) #so you can access it again
```
